%!TEX root = main.tex
% Conclusion
% * Describe each problem, research design, and findings (ans to prob)
% * Recommendations
\chapter{Future Work} % (fold)
\label{cha:future_work}

\section{Convolutional Neural Network}

One possible improvement would be to tailor and train the parameters of the
Convolutional Network to best fit our data. However, this requires a much
larger dataset of labeled images. Therefore, we need to increase the size of
our dataset.

In order to properly evaluate the new system's performance, we should use the
SIFT algorithm in the previous system as our baseline. We have already
generated the SIFT objects representing each image available in the system,
however, they are generated from fiducial points that are manually marked
so that it is able to acheives 99.99\% ranking accuracy. With such bias, it is
hard to evaluate the relative performance between the new and the old systems.

Further, we can evaluate the performance of the model by analyzing the receiver
operating characteristics, or ROC curves, which illustrates the
performance of a classifier model. ROC exhibits the relationship between true
positive rate (TPR) and the false positive rate (FPR), which provides tools to
select possibly optimal models and to discard suboptimal ones.

Since the datasets contain human input, the manually input data can be
utilized to improve the identification results as one of the features. The
number of human interactions depends on the action required to
complete a specific classification task. For instance, if the classification
task requires users to click on the photos, the number of user clicks will then
determine the number of human interactions. The classification results of the
completely automated feature extractor and semi-automated feature extractor
should be compared to determine the optimal level of human involvement.

% chapter future_work (end)
